\emeszida

### 2024-03-29 sigbovik/paper.tex
s/cunei/cuneo/

\section{Description of the Texts}
The Sealand corpus contains numerous fragments implementing recognizable procedures such as bit-shifting, populating an array, computing dot products, and so on. 
However, only a single text is known to have been preserved in its entirety.\footnote{All of the known texts are reproduced in \url{github.com/MrLogarithm/emeszida/tree/main/programs}, and the long text is reproduced in facsimile in the appendix of this work.}
Spanning close to 1700 lines, this impressive text is divided into five sections implementing what modern readers will immediately recognize to be a multi-layer perception.
The first section straightforwadly defines a matrix-multiplication subroutine. 
This is called by a subroutine defined in section two, which applies each layer of the perceptron to a given input, and applies a ReLU-style activation between each pair of layers.
Section three implements the tablet's ``main'' method, which loads an input to memory, calls the perceptron subroutine, and prints the resulting output.
Section four loads the model parameters, which appear to comprise weight matrices of sizes $50\times 2$, $25\times 50$, and $1\times 25$, plus bias vectors of sizes $50$, $25$, and $1$ respectively.
The final section lists pairs of inputs, whose values (incredibly!) correspond to the second and third columns of Plimpton 322.
Interestingly, this section very closely resembles the tables of parameters found in later astronomical calculations (see Figure \ref{fig:BM_34580}).

>>>>

\section{Description of the Texts}
The cuneogramming corpus contains numerous fragments implementing recognizable procedures such as bit-shifting, populating an array, computing dot products, and so on. 
However, only a single text is known to have been preserved in its entirety.\footnote{All of the known texts are reproduced in \url{github.com/MrLogarithm/emeszida/tree/main/programs}, and the long text is reproduced in facsimile in the appendix of this work.}
Spanning close to 1700 lines, this impressive text is divided into five sections implementing what modern readers will immediately recognize to be a multi-layer perception.
The first section straightforwadly defines a matrix-multiplication subroutine. 
This is called by a subroutine defined in section two, which applies each layer of the perceptron to a given input, and applies a ReLU-style activation between each pair of layers.
Section three implements the tablet's ``main'' method, which loads an input to memory, calls the perceptron subroutine, and prints the resulting output.
Section four loads the model parameters, which appear to comprise weight matrices of sizes $50\times 2$, $25\times 50$, and $1\times 25$, plus bias vectors of sizes $50$, $25$, and $1$ respectively.
The final section lists pairs of inputs, whose values (incredibly!) correspond to the second and third columns of Plimpton 322.
Interestingly, this section very closely resembles the tables of parameters found in later astronomical calculations (see Figure \ref{fig:BM_34580}).
